Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide Layers

### 2024-10-28 doc/presentations/defensio/defense.tex
first ugly defensio draft

%01. title slide 
	%- aufhänger
%02. agenda
%03. background info
%04. hypothesis 
%05. manual methods
%06. computational pipeline 
%07. results measuring 
%08. results EMMA 
%09. comparison with other statistics 
%10. summary 
%11. conclusion 
%12. end

@@

\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169

@@

	%% ====== title page ======
	\title{Particle Swarm Optimization of Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

	%% ====== title page ======
	\subtitle{PSO for Steel Passivation with ZrO}  %% (optional) Subtitle, comment out to avoid include
	\newcommand{\authorText}{Johann Dorn}				%% (optional) Author
	\newcommand{\logoTitleFooterR}{grey}  %% (optional) additional logo in title page footer, most right
	\newcommand{\logoTitleFooterM}{grey}  %% (optional) additional logo in title page footer, more right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
	\newcommand{\logoTitleFooterL}{grey}  %% (optional) additional logo in title page footer, right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)

	%% ====== footer ======
	\newcommand{\textFooter}{\subtitle - \authorText} %% (optional) Text for footline, e.g. title, comment out lines to avoid include, max. 1 line
	\newcommand{\slideNumberLabelFooter}{Slide}    	%% Page/Slide/Folie/Seite
%	\date{November 2017}              									%% Date, comment out to get current date

@@

@@

%% ====== Slides ======

\begin{graphicsFrame}{Layout ``Body with figure, small right''}{short}{0.63}{left}{graphic_rs}{\textcopyright~Universität Wien/derknopfdruecker.com}

@@

>>>>

@@

%\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t, draft]{beamer}  %% Choose aspectratio=43 or aspectratio=169
\documentclass[hyperref={pdfpagelabels=false}, aspectratio=43, t]{beamer}  %% Choose aspectratio=43 or aspectratio=169

@@

	%% ====== title page ======
	\title{Particle Swarm Optimization for Chemical Passivation of Steel Substrate with Zirconium Oxide Layers} %% Presentation Title
	\newcommand{\titleBackground}{2}    						%% Background graphic: 0 = no; 1 = yes; 2 = yes with more text space
	\newcommand{\gPath}{figures/}									%% set graphics path
	\newcommand{\graphicsTitleBackground}{title}    %% Filename of background graphic

@@

	%% ====== title page ======
	\subtitle{PSO for Steel Passivation with ZrO}  %% (optional) Subtitle, comment out to avoid include
	\newcommand{\authorText}{Johann Dorn}				%% (optional) Author
%	\newcommand{\logoTitleFooterR}{grey}  %% (optional) additional logo in title page footer, most right
%	\newcommand{\logoTitleFooterM}{grey}  %% (optional) additional logo in title page footer, more right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)
%	\newcommand{\logoTitleFooterL}{grey}  %% (optional) additional logo in title page footer, right (if horizontal spacing not adequate, save multiple logos in one file, use \logoTitleFooterR)

	%% ====== footer ======
	\newcommand{\textFooter}{\subtitle - \authorText} %% (optional) Text for footline, e.g. title, comment out lines to avoid include, max. 1 line
	\newcommand{\slideNumberLabelFooter}{Slide}    	%% Page/Slide/Folie/Seite
	\date{2024-10-30} %% Date, comment out to get current date

@@

\usepackage{siunitx}
\usepackage{chemformula}

@@

%% ====== Slides ======
%TODO: - read aqua/good recipe/mars paper
%01. title slide 
	% - aufhänger
	% - AI and PV
	% - Lab or Computer 
%02. agenda
	% - more like process  from beginning to finish
%03. background info
	% - PV CIGS substrate % https://de.wikipedia.org/wiki/Chalkopyrit
	% https://en.wikipedia.org/wiki/Copper_indium_gallium_selenide_solar_cell
\begin{textFrame}
	{Copper indium gallium selenide solar cell}
	{1}{}
%	\begin{itemize}
%		\item lorem
%		\item ipsum
%		\item \dots
%	\end{itemize}
\begin{table}[tbh]
	\small
    \center
%	\iffalse
	\resizebox{\textwidth}{!}{
		\begin{tabular}{cccccc}
			\hline
			\hline
			Material&   Type&    Band Gap [eV]&    $\lambda$ [nm]&    Abs. coef. $\alpha$ [cm$^{-1}$]    &Penetration Depth [$\mu$m]\\
			\hline
			c-Si&   indirect&   1.12&   600&    \num{4000}&    2.5\\
			c-Si&   indirect&   1.12&   1000&    \num{64}&    150\\
			c-Si&   indirect&   1.12&   1100&    \num{3.5}&    290\\
			a-Si&   direct&      1.7&    600&    \num{40000}&  0.25\\
			CdTe&   direct&      1.45&    600&    \num{37000}&  0.3\\
			GaAs&   direct&      1.42&    600&    \num{40000}&  0.2\\
			\hline
			\hline
		\end{tabular}
	}
    \caption{Photonic properties of several established PV materials (\cite{mertens2020photovoltaik})}
	\label{tab:cigs:alpha}
%	\fi
%
	\resizebox{.45\textwidth}{!}{
    \begin{tabular}{cccc}
        \hline\hline
		Empirical Formula&   Band Gap [\si{eV}{}]\\
        \hline
		\ch{CuInSe2}&  1.04\\
		\ch{CuInS2}&  1.5\\
		\ch{CuGaSe2}&  1.7\\
		\ch{CuGaS2}&  1.55\\
        \hline\hline
    \end{tabular}
}
    \caption{Band gaps of different chalcopyrites (K. Mertens 2015 "Photovoltaik")}
\end{table}
\end{textFrame}

\begin{graphicsFrame}{Copper Indium Gallium Sulfide}{}{0.37}{left}{cigs}{Rau, Schock (2013) "Solar Cells"}
		\begin{itemize}
			\item Abgeschieden wohnen sie in Buchstab-hausen an der Küste des Semantik, eines großen Sprachozeans.
			\item Ein kleines Bächlein namens Duden fließt durch ihren Ort und versorgt sie mit den nötigen Regelialien.
		\end{itemize}
\end{graphicsFrame}

\begin{graphicsFrame}{CIGS modules}{}{0.1}{}{cigs_mod}{}

\end{graphicsFrame}
%04. hypothesis 
%05. manual methods
	% - precursor solution preparation 
		% Anwar 2017 https://iopscience.iop.org/article/10.1088/1757-899X/257/1/012087
		% Hu 2016 https://www.sciencedirect.com/science/article/abs/pii/S0272884216312548
\begin{frame}{test}

\begin{table}[h]
	\center
	\caption{Composition of different buthanolic solutions}
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\ch{BuOH} [ml]	&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\ch{ZrPro} [ml]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\ch{AcAc} [ml]	&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\ch{IPO}/\ch{AcOH} [ml]	&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}
\end{frame}

	% - doctor blading = tape castig 
	% - calcination 
\begin{frame}{Tape casting and Calcination}
	\begin{itemize}
		\item doctor blading construction 
		\item calcination infos (max temperatur, heating rate)
	\end{itemize}
\end{frame}
	% - sputtering contacts
	% - measuring current-voltage characteristics
\begin{frame}{Sputtering and I-V measurement}
	\begin{itemize}
		\item Aluminium Contact through mask
		\item Silver paste
	\end{itemize}
\end{frame}
%06. computational pipeline 
	% - PSO + MARS = EMMA
	% PSO https://doi.org/10.1109/CEC.2010.5586165
\begin{frame}{EMMA = PSO + MARS}
	\begin{itemize}
		\item Particle Swarm Opitimisation 
	\end{itemize}
\end{frame}
%07. results measuring 
	% - SEM % check which sample 
\begin{graphicsFrame}{SEM micrographs}{}{0.37}{right}{sem}{}
		\begin{itemize}
			\item (a) first recipe on FTO
			\item (b) 10 layers on steel
			\item (c) cross section of 5 layers on FTO
			\item (d) side view of scratched layer on steel
		\end{itemize}
\end{graphicsFrame}

	% - I-V % https://en.wikipedia.org/wiki/Current%E2%80%93voltage_characteristic
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv1}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv2}{}\end{graphicsFrame}
\begin{graphicsFrame}{I-V characteristics}{}{0.1}{}{iv3}{}\end{graphicsFrame}
	% - EMMA 
%08. results EMMA 
\begin{graphicsFrame}{Pin Hole Density}{}{0.1}{}{phd}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.1}{}{leakage_w}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{-1}{}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.24}{right}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{Leakage Current}{}{0.37}{right}{leakage}{}\end{graphicsFrame}
\begin{graphicsFrame}{EMMA generations}{}{0.1}{}{emma-gen}{}\end{graphicsFrame}
	% - gen 
%09. comparison with other statistics 
	% - comparing with other stats
	\begin{frame}{Comparison with Statistics}
\begin{table}[htb]
	\centering
%    \caption{Post EMMA vergleich}
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
}
	\vspace{1em}
    %
	\resizebox{.95\textwidth}{!}{
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
\end{frame}

%10. summary 
	% - created ZrO2
	% - optimized with EMMA
	% - double checked with stats
%11. conclusion 
%12. end

\iffalse
\begin{graphicsFrame}{Layout ``Body with figure, small right''}{short}{0.63}{left}{graphic_rs}{\textcopyright~Universität Wien/derknopfdruecker.com}

@@

\fi
